A cross-benchmark comparison of Learning to Rank methods

### 2014-05-16 cikm_paper/paper.tex
Index term
formule past :)

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{}

\keywords{}

@@

$I_{\{M_i(j)>M_k(j)\}} = \begin{cases}
1 & \text{if } M_i(j) \text{ and } M_k(j) \text{ are both defined and } M_i(j) > M_k(j), \\
0 & \text{otherwise}
\end{cases}$\\

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure*}

>>>>

% A category with the (minimum) three required fields
\category{H.3.3}{Information Systems}{Information Storage and Retrieval}[Information Search and Retrieval]

\keywords{Learning to rank, Information retrieval, Benchmark datasets}

@@

\[
I_{M_i(j)>M_k(j)} = \begin{cases}
1 & \parbox[t]{5cm}{if $M_i(j)$ and $M_k(j$ are both defined and $M_i(j) > M_k(j)$,}\\
0 & \parbox[t]{5cm}{otherwise}
\end{cases}
\]

@@

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg3_winnum}
\caption{NDCG@3 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg3}
\end{figure*}

@@

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg5_winnum}
\caption{NDCG@5 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg5}
\end{figure*}

@@

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/ndcg10_winnum}
\caption{NDCG@10 comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_ndcg10}
\end{figure*}

@@

\begin{figure*}[!htp]
\includegraphics[scale=0.285]{gfx/map_winnum}
\caption{MAP comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_map}
\end{figure*}

@@

\begin{figure*}[!htp]
\includegraphics[scale=0.33]{gfx/combined_normalized_winnum}
\caption{Cross-benchmark comparison of Learning-to-Rank methods}
\label{fig:normalised_winning_number_all}
\end{figure*}
